Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-01 paper/paper.tex
macros update

\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are popular tools to
defend against network attacks. These systems monitor the network
traffic and flag suspicious network behavior. Rule-based \nids\ do
that by checking the network traffic against a set of rules, which
become obsolete as attackers learn new strategies to circumvent
existing defenses. This paper proposes \tname{}, a novel approach to
synthesize rules for \textit{rule-based} \nids. \tname\ leverages
malicious (positive) and benign (negative) traffic 
%\rui{positive and negative traffic are first introduced here, withuot being explaiend.} 
and examples of trusted rules to create
rules for new attacks. \tname{} is organized as a pipeline of three components that
1)~create an over-specified seed rule, 2)~derive plausible rules from
the seed, and 3)~rank plausible rules. Experimental results provide
evidence that \tname\ is promising.
 \rui{the example is interesting, but this gives the 
feeling that the work is too preliminary} 
For example, it was
able to synthesize the correct rule in all cases we analyzed and
ranked the correct rule among the first five rules of the reported
ranking in \percTopFiveRanking\ of the cases.
\end{abstract}

@@

%\Mar{@Lucas, please look for constant
  %numbers as this *in text* and use macros instead. We do not want to
  %leave inconsistent data in the paper!}
We evaluated \tname\ against \totalAttacks attacks of various kinds, such as 
\Luc{This is already on section V, should it also be here?} Denial-of-Service (DoS)~\cite{denial-of-service},
Active Reconnaissance (AREC)~\cite{active-reconnaissance} and Privilege
escalation (PESC)~\cite{privilege-escalation}. %\Fix{...}\rui{add few examples}. 
The observed results are encouraging. For 
example, \tname\ ranked the correct rule among the top five rules in \Fix{fix values}
\percTopFiveRanking\ of the cases and ranked the correct rule among 
the top ten rules in \topTenAttacks of the \totalAttacks cases. \rui{to discuss, I find 
this a bit weak.}\Mar{agree. let us try to add more examples and data.}

@@

Overall, results show that \tname\ performed very well in most of the
cases. It reported the ground truth rule in \emph{all} cases and
reported that rule within the top five rules of the ranking in
\percTopFiveRanking\ of the cases.

@@

\emph{ \textbf{Summary of results:}~\tname\ successfully synthesizes
  the golden rules in all cases and that rule is ranked among the top
  five rules in \percTopFiveRanking\ of the cases.  }

@@

Network Intrusion Detectors are an important defense mechanism against
networks attacks. Generating rules to capture new attacks can be
time-consuming and error-prone. This paper presents \tname{}, a novel
approach to generate rules for Rule-based \nids. \tname\ leverages
positive and negative traffic and examples of trusted rules to
synthesize rules. \tname{} is organized as a pipeline of three
components that 1)~create an over-specified seed rule, 2)~derive
plausible rules from the seed, and 3)~rank plausible
rules. Experimental results provide early evidence showing that
\tname\ is promising. It was able to rank the correct rule among the
first five rules of the reported ranking in \percTopFiveRanking\ of
the cases we analyzed, for example. The data set containing our
experimental artifacts is publicly accessible at \ourdataset.

>>>>

\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are popular tools to
defend against network attacks. These systems monitor the network
traffic and flag suspicious network behavior. Rule-based \nids\ do
that by checking the network traffic against a set of rules, which
become obsolete as attackers learn new strategies to circumvent
existing defenses. This paper proposes \tname{}, a novel approach to
synthesize rules for \textit{rule-based} \nids. \tname\ leverages
malicious (positive) and benign (negative) traffic 
%\rui{positive and negative traffic are first introduced here, withuot being explaiend.} 
and examples of trusted rules to create
rules for new attacks. \tname{} is organized as a pipeline of three components that
1)~create an over-specified seed rule, 2)~derive plausible rules from
the seed, and 3)~rank plausible rules. Experimental results provide
evidence that \tname\ is promising.
 \rui{the example is interesting, but this gives the 
feeling that the work is too preliminary} 
For example, it was
able to synthesize the correct rule in all cases we analyzed and
ranked the correct rule among the first ten rules of the reported
ranking in \percTopFiveRanking\ of the cases.
\end{abstract}

@@

%\Mar{@Lucas, please look for constant
  %numbers as this *in text* and use macros instead. We do not want to
  %leave inconsistent data in the paper!}
We evaluated \tname\ against \totalAttacks attacks of various kinds, such as 
\Luc{This is already on section V, should it also be here?} Denial-of-Service (DoS)~\cite{denial-of-service},
Active Reconnaissance (AREC)~\cite{active-reconnaissance} and Privilege
escalation (PESC)~\cite{privilege-escalation}. %\Fix{...}\rui{add few examples}. 
The observed results are encouraging. For 
example, \tname\ ranked the correct rule among the top ten rules in \Fix{fix values}
\percTopFiveRanking\ of the cases \Fix{and ranked the correct rule among 
the top ten rules in \topTenAttacks of the \totalAttacks cases.} \rui{to discuss, I find 
this a bit weak.}\Mar{agree. let us try to add more examples and data.}

@@

Overall, results show that \tname\ performed very well in most of the
cases. It reported the ground truth rule in \emph{all} cases and
reported that rule within the top ten rules of the ranking in
\percTopFiveRanking\ of the cases.

@@

\emph{ \textbf{Summary of results:}~\tname\ successfully synthesizes
  the golden rules in all cases and that rule is ranked among the top
  ten rules in \percTopFiveRanking\ of the cases.  }

@@

Network Intrusion Detectors are an important defense mechanism against
networks attacks. Generating rules to capture new attacks can be
time-consuming and error-prone. This paper presents \tname{}, a novel
approach to generate rules for Rule-based \nids. \tname\ leverages
positive and negative traffic and examples of trusted rules to
synthesize rules. \tname{} is organized as a pipeline of three
components that 1)~create an over-specified seed rule, 2)~derive
plausible rules from the seed, and 3)~rank plausible
rules. Experimental results provide early evidence showing that
\tname\ is promising. It was able to rank the correct rule among the
first ten rules of the reported ranking in \percTopFiveRanking\ of
the cases we analyzed, for example. The data set containing our
experimental artifacts is publicly accessible at \ourdataset.
